Minimizing Time Required For Graduation

### 2010-12-05 paper/paper.tex
fixed some weasel words

Our goal is to determine a schedule of classes from some starting point to
graduation that given the above properties minimizes the total number of
quarters needed. Slightly more formally we would like to: \\ Minimize the total
number of quarters needed to graduate subject to: \begin{enumerate} \item Only
taking courses during quarters they are available \item Only taking a course
once \item Never exceeding a preset number of credit hours per quarter \item
Never taking more than one class at a given time \item Always satisfying
a course's prerequisites prior to taking that course \end{enumerate}

>>>>

Our goal is to determine a schedule of classes from some starting point to
graduation that given the above properties minimizes the total number of
quarters needed. Explicitly: \\ Minimize the total
number of quarters needed to graduate subject to: \begin{enumerate} \item Only
taking courses during quarters they are available \item Only taking a course
once \item Never exceeding a preset number of credit hours per quarter \item
Never taking more than one class at a given time \item Always satisfying
a course's prerequisites prior to taking that course \end{enumerate}
